A Rough Guide to Pre-processing High-Frequency Animal Tracking Data

### 2020-11-11 05_calibration_data.Rmd
add box around inset region

```{r echo=FALSE}
# plot filtered data
fig_speed_outliers <-
  ggplot()+
  geom_point(data = data,
             aes(x, y, 
                 col = speed_in < 25.6),
             size = 0.3, alpha = 0.5,
             show.legend = F)+
  scale_color_manual(values = c("grey", pal[3]))+
  ggthemes::theme_few()+
  theme(axis.text = element_blank(),
        axis.title = element_blank())+
  ggspatial::annotation_scale(location = "tl")+
  coord_sf(crs = 32631)+
  labs(colour = "speed (m/s)")

>>>>

```{r echo=FALSE}
# plot filtered data
fig_speed_outliers <-
  ggplot()+
  geom_point(data = data,
             aes(x, y, 
                 col = speed_in < 25.6),
             size = 0.3, alpha = 0.5,
             show.legend = F)+
  annotate(geom = "rect",
           xmin = 650785, xmax = 653250,
           ymin = 5904450, ymax = 5906133,
           fill = NA, col = "black")+
  scale_color_manual(values = c("grey", pal[3]))+
  ggthemes::theme_few()+
  theme(axis.text = element_blank(),
        axis.title = element_blank())+
  ggspatial::annotation_scale(location = "tl")+
  coord_sf(crs = 32631)+
  labs(colour = "speed (m/s)")
